Investigating the impacts of COVID-19 on team wins and social media engagement in the EPL and Manchester United

### 2022-04-28 outputs/paper/paper.Rmd
This is the last commit as one of the references were missing so I had to go back and include it again.

# Introduction
The English Premier League is renowned to be one of the most watched soccer leagues in the world. To date, the league is broadcasted in over 200 countries which spans over 4 billion people (@citeRichards). With such a large market, teams in the EPL are continually able to attract some of the best players in the world. This is pivotal because, not only will the league be attracting more engagement, but the level of competition will be more intense. At the start of 2020, the COVID-19 pandemic had halted a lot of major activities around the world. With the virus spreading quick, the organizers of the EPL halted the premier league football from March, 2020 to June, 2020. After the initial suspension of the games, teams were allowed to play again but behind closed doors meaning no attendance and stricter protocols. We chanced upon an article on ESPN, that essentially highlights the loss of home advantage arising from games with no fans. Pivotally, they pointed out that Liverpool, who were the 2019-2020 season winners, had lost 6 games at home during the COVID era. Prior to that, they were on a 68 games win streak at home (@citeHamilton). We use @citetidyverse, @citegridExtra, @citehrbrthemes, @citefitdistrplus, @citereadxl and @citerms to prove how Covid has affected teams in the EPL both on and off the field. With the help of @citeknitr, this paper was made possible to print in a pdf format.

>>>>

# Introduction
The English Premier League is renowned to be one of the most watched soccer leagues in the world. To date, the league is broadcasted in over 200 countries which spans over 4 billion people (@citeRichards). With such a large market, teams in the EPL are continually able to attract some of the best players in the world. This is pivotal because, not only will the league be attracting more engagement, but the level of competition will be more intense. At the start of 2020, the COVID-19 pandemic had halted a lot of major activities around the world. With the virus spreading quick, the organizers of the EPL halted the premier league football from March, 2020 to June, 2020. After the initial suspension of the games, teams were allowed to play again but behind closed doors meaning no attendance and stricter protocols. We chanced upon an article on ESPN, that essentially highlights the loss of home advantage arising from games with no fans. Pivotally, they pointed out that Liverpool, who were the 2019-2020 season winners, had lost 6 games at home during the COVID era. Prior to that, they were on a 68 games win streak at home (@citeHamilton). We used @citetidyverse, @citegridExtra, @citehrbrthemes, @citefitdistrplus, @citereadxl and @citerms to prove how Covid has affected teams in the EPL both on and off the field. The graphs were printed using @citeggplot2 With the help of @citeknitr, this paper was made possible to print in a pdf format.
